% mainfile: ./cv.tex
\begin{itemize}
\item
  \ressubheading{Virginia Tech}{Arlington, VA}{GRA, Discovery Analytics 
      Center. Advisor: Dr. Naren Ramakrishnan}{Fall 2014 - Current}\vspace{0.5em}
  \begin{itemize}
    \resitem{Working on Abstractive News Headline Generation in collaboration with \textit{The Washington Post} using Attention-Based Encoder-Decoder models. (Current)}
    \resitem{Built a model in \textit{Python} and \textit{R} for forecasting the number of clicks that an article would receive after a day using early signals that we collect from it after 30 minutes of its publication. This model is an online tool, already being used in \textit{The Washington Post} for predicting the popularity of news articles.}
    \resitem{Built a model for forecasting the shape of the news article views and peak time of news article views. This model is at the development phase in \textit{The Washington Post} and will be implemented and used along side the popularity prediction module.}
    \resitem{Working on prediction of venues daily/weekly wine consumption in collaboration with \textit{Sestra Systems}. We are building a model for predicting the demand for each venue using a combination of HMM, Regression, and Motif Clustering.}
    \resitem{Analyzed the effect of open source datasets like daily price of commodities from \textit{Premise} and internet traffic on websites from \textit{Akamai} on predicting the Domestic Political Crisis in Latin America countries.}
    \resitem{Collaborated on an analysis of the network of entrepreneurs on \textit{VT} campus in Blacksburg and Roanoke area based on the Twitter Follower-Followee network.}
  \end{itemize}\vspace{0.5em}

\item
  \ressubheading{Verisign Labs}{Reston, VA}{Summer Intern, mentored by Galileo Namata}{May 2014}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on understanding Corporate Family Trees using community detection on noisy hypergraphs.}
  \end{itemize}\vspace{0.5em}
\item
  \ressubheading{Virginia Tech}{Blacksburg, VA}{GTA in Dept.\ of Computer 
      Science. Instructor: Dr. Cliff Shaffer}{Fall 2013 - Spring 2014}\vspace{0.5em}
  \begin{itemize}
    \resitem{Grading and tutoring duties for Data Structure in Java class of $\approx$ 100 students.}
  \end{itemize}\vspace{0.5em}

\item
  \ressubheading{Mobin Research Center}{Tehran, Iran}{Java Programmer}{Summer 2013}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on online clustering and classification of massive news feed streams on a distributed framework using \textit{Apache Hadoop}, \textit{Apache Lucene} and \textit{Mahout}.}
    \resitem{Implemented an online short text clustering in \textit{Java} based on \textit{Wordnet} dataset and different text corpuses like news wire corpus.}
    \resitem{Generated the dependency management module of the project using Maven}
  \end{itemize}

\item
  \ressubheading{Wikifegh}{Tehran, Iran}{Research Intern}{Winter 2012}\vspace{0.5em}
  \begin{itemize}
    \resitem{Querying and mining attributed social networks, Wikifegh social network.}
    \resitem{Implemented a visualization module in \textit{JSP} that can represent the connections among different entities of the network in a more comprehensive way than a database table to the system administrator.}
  \end{itemize}

\item
  \ressubheading{Security Operation Centre Project}{Tehran, Iran}{Researcher}{Winter 2011-Winter 2012}\vspace{0.5em}
  \begin{itemize}
    \resitem{I was part of a team that Designed and Implemented an Intelligent Correlation Engine for the Security Operation Center (SOC) and Investigating the Performance of Correlation Engine and Knowledge Base Altogether.}
    \resitem{Implemented a module for Event Correlation using Frequent Pattern Mining in Data Streams.}
  \end{itemize}

\item
  \ressubheading{Netbarg.com}{Tehran, Iran}{Web Developer}{Fall 2011}\vspace{0.5em}
  \begin{itemize}
    \resitem{Implemented the access control module using the ACL (Access Control List)}
    \resitem{Implemented the SMS sender and massive email distribution module using the MailChimp service}
  \end{itemize}

\end{itemize}


